On Secure Delegation of SampBQP with a Classical Client

### 2019-11-23 hamiltonian.tex
Restructure flow and add TODOs
Work on Hamiltonian theorem statement

Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.

@@

We define and construct an instance of Local Hamiltonian that encodes the history of the computation.

\begin{definition}
	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item 0 eigenvalue ground state and has certain form TODO type it out
		\item at least whatever eigenvalue in all other dimensions
		\item has ground state of a particular form we like
	\end{itemize}
\end{definition}

TODO Theorem statement for XZ LH and whatnot

>>>>

Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper. We begin by proving that we can assume without loss of generality that the circuit is of a particular form.

TODO move subsection.

@@

We define and construct an instance of Local Hamiltonian that encodes the history of the computation. TODO This only works for circuits of a particular form...

\begin{definition}
	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item It has an eigenvector $\ket{\psi_{C(x)}}=TODO$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

We'll prove the following theorems in this section.

\begin{theorem}
	Given $C$ and $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\begin{theorem}
	For any given circuit and input, there exists an algorithm that accepts state with probability... TODO
\end{theorem}

Before we present their proofs, first we make an observation.

\begin{observation}
	Given $C$ and $x$, one can first pad $C$ with identity matrices at the end.
\end{observation}

TODO Observation given circuit, if one pads the circuit to obtain... one can measure final state from this by padding...
